Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-07 paper/paper.tex

This section reports the failures observed when running a test suites
on an engine for which those tests were not run
before. Table~\ref{tab:cross-testing} shows the number of failures for
each pair of test suite and engine. The first column shows the test
suites whereas the first row shows the engines. We use a dash (``-'')
to indicate that we did not consider the combinations that associated
a test suite with the engine that originated them; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We also discarded such test cases from
consideration in other engines as we wanted the test to pass on its
originating engine; a failure in that case would be a stronger
indicative of a bug.

To sum, we observed that, considering this dataset, the Mozilla
\smonkey\ was the engine that failed the least whereas the Microsoft
engine \chakra\ failed the most. The \smonkey\ test suite also
revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}). This suggests that the investiment in
testing paid off in this case.

>>>>

This section reports the results of test transplantion, \ie{}, we
analyzed the failures observed when running a test suite on an engine
other than the engine where the test suite
originated.

Table~\ref{tab:cross-testing} shows the number of failures for each
pair of test suite and engine. The first column shows the test suites
and the first row shows the engines that run those tests. We use a
dash (``-'') to indicate that we did not consider the combinations
that associated a test suite with its parent engine; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We did not run the test cases that
fail on its parent engine in any other engines; we wanted all tests to
pass on their parent engine as a failure in that case would be a
stronger indicative of a bug. In total, 64 test cases were discarded
for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
tests (\ie{}, 28369-31276-64) were considered in this experiment.  We
observed from the table that, considering this dataset, the Mozilla
\smonkey\ was the engine that failed the least whereas the Microsoft
engine \chakra\ failed the most. The \smonkey\ test suite also
revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}). This suggests that the investiment in
testing paid off in this case.
